---
title: "spatstat: Demo"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(04062021)
library(spatstat)
```

This demo will explore point process features in the `spatstat` package.

For additional `spatstat` details run the following code `vignette('getstart')` in your R console.

#### 1. Generate Point Process Data

Note this will require both a $n$ and $\boldsymbol{s}$

```{r}
lambda <- 100
n <- rpois(1, lambda)

x <- rbeta(n, 5, 5)
y <- rbeta(n, 5, 5)

hucks <- sample(c('few','some','many'), n, replace = T)
sim_pp <- ppp(x, y, window = owin(xrange = c(0,1), yrange = c(0,1)), marks = hucks)
plot(sim_pp, main = 'simulated huckleberry map')
```

There are also a collection of methods in spatstat to simulation random point process, see `rpoispp` or many others.

Note `spatstat.data` has a large collection of point process datasets.

#### 2. Summarize Point Process

```{r}
summary(sim_pp)
```


#### 3. Assess Spatial Structure

Remember, the $F$ function corresponds to empty space and $G$ corresponds to nearest neighbor space.

```{r}
plot(envelope(sim_pp,Fest))
plot(envelope(sim_pp,Gest))
```

The envelope procedure compares the observed results with a set of simulated homogeneous point processes.

#### 4. Modeling Intensity

```{r}
plot(density(sim_pp))

ppm(unmark(sim_pp) , ~1, Poisson())

ppm(unmark(sim_pp) , ~x  + y, Poisson())
  
```

